Time slice analyses

### 2017-09-05 analyses/02-time-slice-analyses.Rmd
Add notes for disparity phase

## Cleaning the tree to remove things that aren't in the matrix 
cleaned_data <- clean.data(matrix$matrix, tree)
tree <- cleaned_data$tree

## Loading the distance matrices
## See "01-extract-data-for analyses.Rmd" for how we made these
load(paste0("data/processed/distance_matrix.", slug ,".Rda"))

@@

time slicing
-----------------------------------

>>>>

## Cleaning the tree to remove things that aren't in the matrix 
cleaned_data <- clean.data(matrix$matrix, tree)
matrix$matrix <- cleaned_data$matrix
tree <- cleaned_data$tree

## Loading the distance matrices
## See "01-extract-data-for analyses.Rmd" for how we made these
load(paste0("../data/processed/distance_matrix.", slug ,".Rda"))

@@

Stratigraphy
-----------------------------------

How to go about that????
Need to collate data ourselves or can we use strap?

Time bins (equal sized)
-----------------------------------

What do we want to vary? Metrics? Number of bins?

Note we might want to exclude node but current won't work due to mismatch - ooh maybe use clean.data to fix??? Yes that works

no.nodes <- clean.data(morphospace, tree)
m<- no.nodes$data

```{r, eval = FALSE}
time.bin.sim <- function(times, metric) {

  sub <- time.subsamples(data = morphospace, tree = tree, method = "discrete",
                time = times, FADLAD = FADLAD, inc.nodes = TRUE)

  disparity <- summary(dispRity(sub, metric = metric),
                      round = 10)
}
```

What outputs do we want?

Time slicing 
-----------------------------------

What do we want to vary? Metrics? Number of slices? Model of evolution

Note we might want to exclude node but current won't work due to mismatch - ooh maybe use clean.data to fix???

```{r, eval = FALSE}
time.slice.sim <- function(times, metric) {

  sub <- time.subsamples(data = morphospace, tree = tree, 
    method = "continuous", model = "gradual", time = times,
    FADLAD = FADLAD, inc.nodes = TRUE)

  disparity <- summary(dispRity(sub, metric = metric),
                      round = 10)
}
```
